\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
complete State of Eye Tracking in HRI

The literature on the

@@

Controlling robot with gaze \cite{bhuiyan2004tracking}

@@

Physiological and subjective evaluation of a human-robot object hand-over task  \cite{dehais2011physiological}

@@

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an eye-tracking
study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation.

>>>>

The usage of eye-tracking methods in HRI is very sparse. It must be noted that to our best knowledge only very few attempts to use eye-tracking as an interaction modality or as an interaction assessment technique in HRI.

@@

To guide the motion of a robot \cite{bhuiyan2004tracking} used real time  gaze data of a human user. The users were able to provide the visual and geometrical motion information to the robot by moving their eyes in different parts of the human-robot interface.

@@

To evaluate the effectiveness of the motion planning algorithm for a robot \cite{dehais2011physiological} used eye-tracking techniques. In an object hand-over task between a robot and a human, the authors compared various motion planning algorithms based on the gaze of the human.

@@

 In an eye-tracking study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation. The video based interaction modality was used by the authors. This constraints the  interaction of the human-robot dyad to just a video. However, the stimulus (video) for eye-tracking provides strong contrast and a good control for experimental conditions.
